Storing messages with multipartite neural cliques

### 2014-07-23 Articles/article.tex
...

	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store it. Note it doesn't take into account how effectively messages are retrieved.

@@

		$R$ can be written $\frac{2H(\mathcal{M})}{c(c-1) \ell^2}$.

		A very good approximation is thereby $R = \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}$.

		The efficiency of the network measures how much information can be retrieved compared to how much could be at the maximum. The efficiency is called $\eta$. $\eta = P_{retrieve} R  h^{-1}$.

@@

	We are interested in distinct problems of messages retrieval. We detail what those problems are. Since those problems vary in hardness, we propose distinct measures for efficiencies. We first compute the rate of the network. Efficiency measures the ratio of information effectively retrieved over the hardness of the problem. It can be expressed in function of the rate $R$, the retrieval rate $P_{retrieve}$ and some measure of hardness of the problem $h$.

@@

	We can extend the mapping $f$ to $\left( \mathcal{A} \cup \{ \intercal \}\right)^c$, by associating to the symbol $\intercal$ a cluster where none of the units are activated. If we consider the binary representation $\mu$ of $m$, erased symbols corresponds to erased clusters. An erased cluster is a cluster where all units are set to $0$. Formally the partial probe $\tilde{\mu}$ is such that for all $j\in [c]$ and $k \in [\ell ]$, \[ 
		\tilde{\mu}[(j-1)\ell+k] = \bigg \{ \begin{array}{cl} 0 & \mbox{if } j\in \{j_1, \dots , j_{c_e} \}\\
													\mu[(j-1)\ell+k] & \mbox{otherwise}	
	\end{array}\]

@@

@@

	The problem of resilience takes into account the possibility for the network of sustaining damages. Despite those, the network can still work as an associative memory, albeit with decreased performance.

>>>>

	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store the network itself. Note it doesn't take into account how effectively messages are retrieved (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)

@@

		$R$ can be written as $\frac{2H(\mathcal{M})}{c(c-1) \ell^2}$.

		A very good approximation is thereby \begin{align}
		R \approx \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}
		\label{rateth}
		\end{align}

		The efficiency of the network measures how much information can be retrieved compared to how much could be at the maximum. The efficiency is called $\eta$. $\eta = P_{retrieve} R  h$.

@@

	We are interested in distinct problems of messages retrieval. We detail what those problems are. Since those problems vary in hardness, we propose distinct measures for efficiencies. Efficiency measures the ratio of information effectively retrieved over the hardness of the problem. It can be expressed in function of the rate $R$, the retrieval rate $P_{retrieve}$ and some measure of hardness of the problem $h$.

@@

	We can extend the mapping $f$ to $\left( \mathcal{A} \cup \{ \intercal \}\right)^c$, by associating to the symbol $\intercal$ an "erased cluster" where none of the units are activated. If we consider the binary representation $\mu$ of $m$, erased symbols corresponds to erased clusters. %An erased cluster is a cluster where all units are set to $0$. 
	Formally the partial probe $\tilde{\mu}$ is such that for all $j\in [c]$ and $k \in [\ell ]$, \[ 
		\tilde{\mu}[(j-1)\ell+k] = \bigg \{ \begin{array}{cl} 0 & \mbox{if } j\in \{j_1, \dots , j_{c_e} \}\\
													\mu[(j-1)\ell+k] & \mbox{otherwise}	
	\end{array}\]

@@

	We compute the probability for a message $m$ and a partial probe $\tilde{m}$ to engender confusion.

	Let $j\not\in \{j_1, \dots , j_{c_e} \}$ be the index of a non-erased symbol in $\tilde{m}$. The probability for another message $m'$ in $\mathcal{M}$ to satisfy $m'_j = \tilde{m}_j$ is $1/|\mathcal{A}| = \binom{l}{a}^{-1}$. As symbols of a message are independent (since messages are uniformly distributed), the probability that for all $j\not\in \{j_1, \dots , j_{c_e} \}$, $m'_{j} = \tilde{m}_j$ is ${\ell \choose a}^{-(c - c_e)}$. Since messages are independent the probability for all other messages in $\mathcal{M}$ not to be equal to $\tilde{m}$ on non-erased symbols is $\left(1-{\ell \choose a}^{-(c - c_e)}\right)^{M-1}$. We define $h_{erasures}$ the hardness of the problem as the inverse of that last probability :

	\begin{align}
		h_{erasures} = \left(1-{\ell \choose a}^{-(c - c_e)}\right)^{-(M-1)}
		\label{herrth}
	\end{align}

	Notice increasing the size of the alphabet makes the problem easier as confusion

@@

	The problem of resilience takes into account the possibility for the network of sustaining damages. Despite those, the network can still work as an associative memory, albeit with decreased performance. The network $W$ first sustains random binary noises of magnitude $\psi$. The new matrix is called $\tilde{W}$ and satisfies for all $i$ and $i'$ in $[c \cdot \ell ]$, %$W_{ii'} = \big \begin{array}{ccc} W & o\end{array}$
